---
params:
  alpha_draw: NA
  graph_data: NA

output: pdf_document
header-includes:
  \usepackage{booktabs}
  \usepackage{fancyhdr}
  \pagestyle{fancy}
  \fancyhead[CO,CE]{Graphapp Draw Report}
---
The inputs in the \textit{Graph} and \textit{Details} parts correspond to the information required for the multiple test procedures. Specifically, the \textit{nodes} correspond to elementary hypotheses: $H_1$, ..., $H_m$ with associated weights denoting the local significance levels $\alpha_1$, ..., $\alpha_m$. In addition, any two vertices $H_i$ and $H_j$ are connected through directed \textit{edges} and the associated weights $g_{ij}$ indicates the fraction of the local significance level $\alpha_i$ that is propagated to $H_j$ once $H_i$ has been rejected. A weight $g_{ij}=0$ indicates that no propagation of the significance level is foreseen and the edge is dopped for convenience.

```{r, echo=FALSE}
library(knitr)
library(xtable)
alpha <- params$alpha_draw
edges <- params$graph_data$edges
nodes <- params$graph_data$nodes
num <- nrow(nodes)
names <- nodes$label
df <- matrix(0,nrow=num,ncol=num)
rownames(df) <- names
colnames(df) <- names
for (i in 1:nrow(edges)){
  df[which(rownames(df)==edges$from[i]),which(colnames(df)==edges$to[i])] <- as.numeric(edges$label[i])
}
```

```{r, echo=FALSE, results='asis'}
rename_nodes <- nodes[,c("label","weight","pvalue")]
colnames(rename_nodes) <- c("hypothesis","weight","pvalue")
t1 <- kable(nodes[,c("label","weight","pvalue")],
            caption = "Nodes")

t2 <- kable(df,caption = "Edges")
t1
t2
# cat(c("\\begin{table}[!htb]
#     \\begin{minipage}{.5\\linewidth}
#       \\caption{Nodes}
#       \\centering",
#         t1,
#     "\\end{minipage}%
#     \\begin{minipage}{.5\\linewidth}
#       \\centering
#         \\caption{Edges}",
#         t2,
#     "\\end{minipage} 
# \\end{table}"
# ))  
```

The results of graphical approaches could be summarized as below:

```{r echo=FALSE,fig.height=3.5}
wp <- matrix(0,nrow=num,ncol=2)
colnames(wp) <- c("weights","pvalues")
rownames(wp) <- names
wp[,"weights"] <- f2d(nodes$weight)
wp[,"pvalues"] <- as.numeric(nodes$pvalue)

net <- network(df,
               directed = TRUE,
               names.eval = "weights",
               ignore.eval = FALSE)
net %v% "vertex.names"  <- names
e <- network.edgecount(net)
      
initial <-  ggplot(net, aes(x = x, y = y, xend = xend, yend = yend)) +
        xlim(-0.05, 1.05) + ylim(-0.05, 1.05)+
        geom_edges(arrow = arrow(length = unit(20, "pt"), 
                                 type = "closed"),color = "grey50",curvature = 0.15) +
        geom_nodes(aes(x, y),color = "grey",alpha = 0.5, size = 14) +
        geom_nodetext(aes(label = vertex.names)) +
        scale_color_brewer(palette = "Set2") +
        labs(title='Initial graph',size=8)+
        theme_blank()+
        theme(aspect.ratio=1,
              plot.title = element_text(size=15, face="bold.italic",
                                        margin = margin(15, 0, 15, 0)),
              plot.margin = margin(0.5,0.1,0.1,0.1))    # t r b l
      
res <- gMCP_app(matrix=df,
                weights=f2d(wp[,"weights"]),
                pvalues=as.numeric(wp[,"pvalues"]),
                alpha = alpha,fweights = F)
res_pvalues <- res$pvalues
res_weights <- res$weights
res_G <- res$G
res_net <- network(res_G,directed = TRUE,
                   names.eval = "weights",ignore.eval = FALSE)
res_net %v% "vertex.names"  <- names
e <- network.edgecount(res_net)
res_net %v% "Rejection" <- (res$rejected)
      
final <- ggplot(res_net, aes(x = x, y = y, xend = xend, yend = yend)) +
        xlim(-0.05, 1.05) + ylim(-0.05, 1.05)+
        geom_edges(arrow = arrow(length = unit(20, "pt"), type = "closed"),
                   color = "grey50",curvature = 0.15) +
        geom_nodes(aes(x, y, colour = Rejection), alpha = 0.5,size = 14) +
        geom_nodetext(aes(label = vertex.names)) +
        scale_color_brewer(palette = "Set2") +
        labs(title='Final graph',size=8)+
        theme(legend.position = "none")+
        theme_blank()+
        theme(legend.position = "none")+
        theme(aspect.ratio=1,
              plot.title = element_text(size=15, face="bold.italic",
                                        margin = margin(10, 5, 10, 0)),
              plot.margin = margin(0.5,0.5,0.1,0.1))

      legend_b <- get_legend(final + theme(legend.position="bottom",
                                           legend.justification="center"))
      
cowplot::plot_grid(initial,final,
                   legend_b, ncol = 2, 
                   rel_heights = c(1, .2))
      
```

```{r, echo=FALSE, results='asis'}
result_rej <- data.frame(res$rejected)
result_rej <- ifelse(result_rej=="TRUE","rejected", "not rejected")
result_adjp <- res$adjpvalues
output <- data.frame(cbind(as.character(names),result_adjp,result_rej))
colnames(output) <- c("hypothesis","adjusted p-value","rejection")
rownames(output) <- NULL
kable(output,caption = "Results of Rejectiona and Adjusted p-values")
```

